Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-03 paper/EDA.qmd
Final go except update to 1.3 1.4

## Data Analysis Method   
We will use **one-way ANOVA** to analyze the effects of different pain relievers on memory performance
Similarly, we will use **two-way ANOVA** to analyze the effects of different dosage levels per drug type on memory performance and cognitive retention.

@@

```{r}
#| echo: false
#| warning: false
#| message: false

@@

kable(improvement_summary, format = "latex", booktabs = TRUE, caption = "Mean Improvement in Game Scores by Drug")

@@

*Independence* For our one-way ANOVA model, we have independence because our observations are independent within and across the groups i.e all participants were randomly assigned a pain reliever, and there was no relationships between observations (i.e repeated  participants, treatments etc.)

@@

*Independence*
For our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.

@@

# Corrected Two-Way ANOVA Model for our reseearch question 2
model_2 <- aov(game_after ~ drug + dosage_level, data = clean_data)

@@

>>>>

## Data Analysis Method   
We will use **one-way ANOVA** to analyze the effects of different pain relievers on memory performance.
Similarly, we will use **two-way ANOVA** to analyze the effects of different dosage levels per drug type on memory performance and cognitive retention.

@@

Evident through the results on @tbl-summary-6, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account). Aspirin appears to negatively impact the results of the game after being given to people, this was seen through the mean and median improvements.

```{r}
#| label: tbl-summary-6
#| tbl-cap: "Mean Improvement in Game Scores by Drug"
#| echo: false
#| warning: false
#| message: false

@@

kable(improvement_summary, format = "latex", booktabs = TRUE)

@@

*Independence:* For our one-way ANOVA model, we have independence because our observations are independent within and across the groups i.e all participants were randomly assigned a pain reliever, and there was no relationships between observations (i.e repeated  participants, treatments etc.)

@@

*Independence:*
For our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.

@@

# Corrected Two-Way ANOVA Model for our research question 2
model_2 <- aov(game_after ~ drug + dosage_level, data = clean_data)

@@

\newpage

# Appendix

```{r}

```{r}

```{r}
# Count and percentage for Drug
drug_counts <- table(clean_data$drug)
drug_percentages <- prop.table(drug_counts) * 100
drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(as.numeric(drug_percentages), 2))
colnames(drug_summary) <- c("Drug", "Count", "Percentage")
kable(drug_summary, format = "latex", booktabs = TRUE) 
```

```{r}

```{r}
# Count and percentage for Age Group
age_counts <- table(clean_data$age_group)
age_percentages <- prop.table(age_counts) * 100
age_summary <- data.frame(Age_Group = names(age_counts), Count = as.numeric(age_counts), Percentage = round(as.numeric(age_percentages), 2))

```{r}

kable(improvement_summary, format = "latex", booktabs = TRUE)

```{r}

p1 / p2 + plot_annotation()
```

```{r}

p1 / p2 + plot_annotation()
```

```{r}

```{r}
#| fig.width: 6
#| fig.height: 4
#| fig-cap: "Normality & Homegenity (Two-way ANOVA)"

# Corrected Two-Way ANOVA Model for our research question 2
model_2 <- aov(game_after ~ drug + dosage_level, data = clean_data)

# Check Model Assumptions
check_model(model_2, check = c("normality", "homogeneity"))
```
